---
title: "ppiAIPW Quickstart"
vignette: >
  %\VignetteIndexEntry{ppiAIPW Quickstart}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(ppiAIPW)

set.seed(1)
Y <- rnorm(80)
Yhat <- Y + rnorm(80, sd = 0.35)
Yhat_unlabeled <- rnorm(200)

result <- mean_inference(
  Y,
  Yhat,
  Yhat_unlabeled,
  method = "monotone_spline",
  alpha = 0.1
)

print(result)
summary(result)
```

All numeric inputs must be finite. The package rejects `NaN`, `NA`, and `Inf`
values in outcomes, predictions, covariates, and weights with clear validation
errors.

`ppiAIPW` is built around a simple workflow:

- call `mean_inference()` when you want estimate, SE, interval, and fitted calibrator together
- use `mean_pointestimate()`, `mean_se()`, or `mean_ci()` for narrower outputs
- use `method = "auto"` when you want a data-adaptive method choice

```{r}
auto_result <- mean_inference(
  Y,
  Yhat,
  Yhat_unlabeled,
  method = "auto",
  candidate_methods = c("aipw", "linear", "monotone_spline", "isotonic"),
  num_folds = 5,
  selection_random_state = 0
)

print(auto_result)
```
